\huge A Better (One-Line!) Title Here

### 2016-10-20 pets2017-paper/pets2017-paper.tex
more coloring for TODOS.

\subsection{Procedure}
The one-hour, single-participant procedure begun when a participant entered a small 
room with a single computer, which is equipped with Tor, Chrome, Firefox, Internet Explorer, and VLC.
Each participant is informed of the risks and purpose of the study.
A researcher informed the participant of the simulated censorship environment and
instruct them to visit sample blocked and unblocked websites
in a standard browser (Appendix~\ref{qualitative-script}). 
This shows participants what a blocked site looks like in a browser. 
Then, the participant was asked to complete a worksheet that gives information
on their censorship environment and instructed them
to visit one blocked website and one non-blocked website (Appendix~\ref{participant-worksheet}).
The worksheet informed the participant that the network is censored,
but did not give details of what services and websites are specifically blocked.
Participants were able to visit the unblocked website using any familiar browser,
but had to configure Tor Browser in order to visit the blocked website.

@@

After participants completed the browsing tasks or ran out of time,
we interviewed them about their experience and
took notes of the questions and answers.
We asked questions asking about their general experience, 
interface features they found confusing, and feedback for improvements (Appendix~\ref{interview-questions}). 
We followed up with specific questions prompted from watching their screen. 
This was to verify any hypotheses we had (e.g. ``they did not know what an ISP was'').
We paid each participant~\$30 for their time.

\subsection{Results} 
We discuss six common challenges our participants encountered during the configuration process.
Participant quotations come from live transcription during the post-experiment interview
and are not necessarily verbatim.\\

@@

\begin{figure}[t]
  \centering
    \includegraphics[width=0.5\textwidth]{error.png}
    \caption{An example of a technical error message which our participants did not understand.}
\label{fig:error}
\end{figure}

%for color red
}

@@

\subsection{Recruitment}
We recruited 124 participants, about 20 for each
condition. We recruited half of our users from Craigslist, and half of our participants from 
the <redacted> %Xlab 
participant pool. Although <redacted> %Xlab 
participants are not limited to <redacted> %UC Berkeley 
students and staff,
a majority of the participants are from campus. For this reason, we chose to recruit 
half of our participants from Craigslist to ensure a diverse set of participants. 
The recruitment text vaguely suggests testing a piece of software, and does not require
that users provide information in advance (Appendix~\ref{quantitative-recruitment}). 
Out of our 124 participants, 59 were recruited from the <redacted> %Xlab 
pool and the other 65 were
recruited from Craigslist. Ages ranged from 18 to~68 years
($\mu = 28.9$, $\sigma = 12$). 56.8\% were male and 
84.8\% of our participants had at least a college education.
}

@@

After users completed the browsing tasks, they took a short exit survey (Appendix~\ref{quantitative-exit-survey})
that collected their demographics. All users were instructed to sit until the end of the experiment,
regardless of when they had completed their task. After the 40 minutes, 
participants were officially informed that their time was up, and were given their payment of 
\$30 for their time.

\subsection{Results} 
The possible interface version and environment combinations resulted in 6 experimental conditions. We recruited 124 participants to aim for about 20 participants per condition. We filtered participants who downloaded their own version of Tor Browser or did not sign the consent form, resulting in 114 participants. Table~\ref{table:participant-summary} summarizes the rate of success, time to success, and active time for our participants' by condition.

>>>>

\subsection{Procedure}
{\color {red}
The one-hour, single-participant procedure begun when a participant entered a small 
room with a single computer, which is equipped with Tor, Chrome, Firefox, Internet Explorer, and VLC.
Each participant is informed of the risks and purpose of the study.
A researcher informed the participant of the simulated censorship environment and
instruct them to visit sample blocked and unblocked websites
in a standard browser (Appendix~\ref{qualitative-script}). 
This shows participants what a blocked site looks like in a browser. 
Then, the participant was asked to complete a worksheet that gives information
on their censorship environment and instructed them
to visit one blocked website and one non-blocked website (Appendix~\ref{participant-worksheet}).
The worksheet informed the participant that the network is censored,
but did not give details of what services and websites are specifically blocked.
Participants were able to visit the unblocked website using any familiar browser,
but had to configure Tor Browser in order to visit the blocked website.

@@

After participants completed the browsing tasks or ran out of time,
we interviewed them about their experience and
took notes of the questions and answers.
We asked questions asking about their general experience, 
interface features they found confusing, and feedback for improvements (Appendix~\ref{interview-questions}). 
We followed up with specific questions prompted from watching their screen. 
This was to verify any hypotheses we had (e.g. ``they did not know what an ISP was'').
We paid each participant~\$30 for their time. 
}

\subsection{Results} 
{\color {red}
We discuss six common challenges our participants encountered during the configuration process.
Participant quotations come from live transcription during the post-experiment interview
and are not necessarily verbatim.\\

@@

\begin{figure}[t]
  \centering
    \includegraphics[width=0.5\textwidth]{error.png}
    \caption{An example of a technical error message which our participants did not understand.}
\label{fig:error}
\end{figure}
}

@@

\subsection{Recruitment}
{\color {red} 
We recruited 124 participants, about 20 for each
condition. We recruited half of our users from Craigslist, and half of our participants from 
the <redacted> %Xlab 
participant pool. Although <redacted> %Xlab 
participants are not limited to <redacted> %UC Berkeley 
students and staff,
a majority of the participants are from campus. For this reason, we chose to recruit 
half of our participants from Craigslist to ensure a diverse set of participants. 
The recruitment text vaguely suggests testing a piece of software, and does not require
that users provide information in advance (Appendix~\ref{quantitative-recruitment}). 
Out of our 124 participants, 59 were recruited from the <redacted> %Xlab 
pool and the other 65 were
recruited from Craigslist. Ages ranged from 18 to~68 years
($\mu = 28.9$, $\sigma = 12$). 56.8\% were male and 
84.8\% of our participants had at least a college education.
}

@@

After users completed the browsing tasks, they took a short exit survey (Appendix~\ref{quantitative-exit-survey})
that collected their demographics. All users were instructed to sit until the end of the experiment,
regardless of when they had completed their task. After the 40 minutes, 
participants were officially informed that their time was up, and were given their payment of 
\$30 for their time. 
}

\subsection{Results} 
{\color {red} 
The possible interface version and environment combinations resulted in 6 experimental conditions. We recruited 124 participants to aim for about 20 participants per condition. We filtered participants who downloaded their own version of Tor Browser or did not sign the consent form, resulting in 114 participants. Table~\ref{table:participant-summary} summarizes the rate of success, time to success, and active time for our participants' by condition.
